% This document provides the style to be used for a MSc Thesis at the
% Parallel and Distributed Systems group
\documentclass[11pt,twoside,a4paper,openright]{report}

% % use babel for proper hyphenation
% \usepackage[dutch,british]{babel}
% \newcommand\fh{\babelhyphen{hard}}
% % Graphics: like the DUT logo on the front cover
% \usepackage[dvips]{graphicx}
% % \usepackage{graphicx}
% % \usepackage{graphicx}
% % \usepackage{graphics}
% \usepackage{eurosym}
% \usepackage{seqsplit}
% \usepackage[hidelinks]{hyperref}
% \usepackage{url}
% \def\UrlBreaks{\do\/\do-}
% \usepackage{breakurl}
%
% \usepackage{titlesec}
% \usepackage{titletoc}
% \usepackage{tabularx}
% \usepackage{changepage}
% \usepackage{tocstyle}

% math packages
\usepackage{amsmath}
\usepackage{amssymb}

% textblocks for title page
\usepackage[absolute]{textpos}

% use babel for proper hyphenation
\usepackage[british]{babel}

% Graphics: different for pdflatex or dvi output, choose one
%%\usepackage[dvips]{graphicx}
%%\usepackage[pdftex]{graphicx}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{epstopdf}
\usepackage{rotating}
\usepackage{subfig}
\usepackage{caption}
\usepackage{epstopdf}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{listings}
\usepackage{cite}
\usepackage{array}
\usepackage{booktabs}
\usepackage[bottom]{footmisc}

\usepackage{eurosym}
\usepackage{seqsplit}
\usepackage[hidelinks]{hyperref}
\usepackage{url}
\def\UrlBreaks{\do\/\do-}
\usepackage{breakurl}
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{tabularx}
\usepackage{changepage}


% FONT: times
\usepackage{times}
% for url's use "\url{http://www.google.com/}"
\usepackage{cite}
\usepackage{amsmath,booktabs}
\usepackage[]{siunitx}
\usepackage{textcomp}

\newcommand\vn[1]{\textsc{\MakeLowercase{#1}}} % "variable name" macro
\newcommand\mc[1]{\multicolumn{1}{c}{#1}} % handy shortcut macro
\newcommand\ID{\mathit{ID}}

\newcommand{\reportTitle}{Open-Source Software-Based SRAM-PUF for Secure Data and Key Storage Using Off-The-Shelf SRAM}
\newcommand{\problemStatement}{How to develop an open-source secure data and key storage scheme using off-the-shelf SRAM component and software-based SRAM PUF technology?}
\newcommand{\reportAuthor}{Ade Setyawan Sajim}
\newcommand{\reportEmail}{AdeSetyawanSajim@student.tudelft.nl}
\newcommand{\reportUrlEmail}{\href{mailto:\reportEmail}{\reportEmail}}
\newcommand{\reportMSC}{MSc Computer Engineering} %{Embedded Systems}{Computer Engineering}{Computer Science}{Electrical Engineering}
\newcommand{\reportDate}{25\textsuperscript{th} April 2018} %TODO: Dit is de datum van uitgifte van final versie aan de afstudeer commissie
\newcommand{\presentationDate}{17\textsuperscript{th} May 2018}
\newcommand{\graduationCommittee}{
Dr. Ir. Johan Pouwelse & Delft University of Technology \\
Dr. Stephan Wong & Delft University of Technology \\
Dr. J.S. Rellermeyer & Delft University of Technology \\
Ir. Haji Akhundov & Delft University of Technology \\
% Dr. RangaRao Venkatesha Prasad 	& Delft University of Technology \\
% Dr. Alessandro Bozzon 			& Delft University of Technology \\
} % The order of listing the names: Graduation prof, supervisor(s), others ordered by title + alphabetical
%examples:
%prof. dr. ir. H. J. Sips (chair) & Delft University of Technology \\
%ir. dr. D. H. J. Epema           & Delft University of Technology \\
\newcommand{\reportAbstract}{
SRAM PUF has a potential to become the main player in hardware security. Unfortunately, currently available solutions are usually locked to specific entities, such as companies or universities. Here, we introduce the first open source project to develop software-based SRAM PUF technology using off-the-shelf SRAM.
We also present testing results on two off-the-shelf SRAMs quality to be a PUF component; Microchip 23LC1024 and Cypress CY62256NLL.
Testing on two bit-selection algorithms (data remanence analysis and neighbor analysis) are also performed.
Based on the testing results, we introduce a PUF enrollment scheme using data remanence analysis as the bit selection algorithm which will locate the location of the stable bits and SRAM Cypress CY62256NLL as the off-the-shelf SRAM.
Moreover, we also propose a procedure to develop SRAM PUF-based applications using any off-the-shelf SRAM. The procedure consists of three main steps; test the off-the-shelf SRAM quality to be a PUF component, create a PUF-generated key using enrollment-reconstruction mechanism, and develop any PUF-based application utilizing the PUF-generated key.
In addition, an idea to create numerous CRPs using SRAM PUF is also proposed here. Using a collection of stable bits as a challenge, the stable bits are permutated among themselves to create a challenge which has a numerous number of possibilities.
Furthermore, we also present a secure data and key storage scheme using SRAM PUF. The proposed scheme is influenced by multi-factor authentication. Using a combination of a PUF-generated key and user's password, a derived key is produced and utilized as the final key to protect user's data or/and user's key.
As the grand concluding experiment of this thesis, we present a demo of storing a private key of Bitcoin.
% We believes this proves the usefulness and viability of this work for realistic use-cases.
We shows that the Bitcoin key will not be reconstructed successfully if user's password is incorrect or the SRAM is not similar with the one that use to encrypt the Bitcoin key.
}
\newcommand{\reportKeywords}{PUF, SRAM PUF, security, key storage, data protection}
\newcommand{\chapterTwo}{Related Work}
% \newcommand{\chapterThree}{SRAM PUF Open Problems}
\newcommand{\chapterThree}{Problem Statement}
\newcommand{\chapterFour}{Proposed System}
\newcommand{\chapterFive}{Implementation, Experiments and Results}
\newcommand{\chapterSix}{Conclusions and Future Work}
\newcommand{\minus}{\scalebox{0.75}[1.0]{$-$}}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\hoffset=1.63cm
\oddsidemargin=0in
\evensidemargin=0in
\textwidth=5in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\parindent=1em

\pagestyle{empty}

% FRONTCOVER
\include{template/frontcover}

% EMPTY PAGE
\cleardoublepage

\pagestyle{plain}

% TITLE PAGE: page i (hidden)
\include{template/titlepage}

% GRADUATION DATA AND ABSTRACT: pages ii and iii (hidden)
\include{template/graduationdata}

\pagenumbering{roman}
\setcounter{page}{4}

% EMPTY PAGE: page iv
\cleardoublepage

% OPTIONAL QUOTATION: page v
%\include{quotation}
% EMPTY PAGE: page vi
%\cleardoublepage

% PREFACE: page v
\include{template/preface}
% EMPTY PAGE: page vi
\cleardoublepage

% TABLE OF CONTENTS: starting at page vii
\tableofcontents

\cleardoublepage

\pagenumbering{arabic}
\setcounter{page}{1}

% INTRODUCTION: page 1
% \include{introduction}

% % CHAPTERS ... For instance: History/Prior Work, Design/Implementation, Experiments
% \include{chapter_2}

\include{chapter/introduction}
% \input{chapter/security}
% \input{chapter/chapter3}
\input{chapter/related_work}
% \input{chapter/related}
% \input{chapter/chapter3}
\input{chapter/proposed}
\input{chapter/experiment}

% CONCLUSIONS AND FUTURE WORK
\include{chapter/conclusion}

% BIBLIOGRAPHY
% \addcontentsline{toc}{chapter}{Bibliography}
% \bibliographystyle{bib/latex8}
\bibliographystyle{unsrt}
% \bibliography{bib/all}
\bibliography{bib/article,bib/book,bib/inbook,bib/inproceedings,bib/misc,bib/mscthesis}


\appendix

\include{template/appendix_a}

\end{document}
